\documentstyle[makeidx]{book}
\input{psfig}
\input{pkarp.mac}
\input{frame.mac}
\input{format_wide_1.5}
\renewcommand{\baselinestretch}{1}

%%\newcommand{\kbfn}[1]{\vspace{.85 in}{\bf #1}}
%%\newcommand{\kbfn}[2]{\vspace{.85 in}\kfn{#1}\ \karg{#2}}
\newcommand{\kbfn}[2]{\vspace{.15 in}\kfn{#1}\ \karg{#2}}
%%nlkbfn is now no longer used.
%%\newcommand{\nlkbfn}[2]{\\ \kfn{#1}\ \karg{#2}} % put a kbfn on a new line
\newcommand{\kfn}[1]{{\bf #1}\index{#1}}	% fn name in text
\newcommand{\karg}[1]{{\bf #1}}			% arg name 
\newcommand{\nikfn}[1]{{\bf #1}}		% non-index fn name in text
\newenvironment{gfpop}[2]{\kbfn{#1}{#2}}{}
\makeindex

\begin{document}

\title{The Generic Frame Protocol 2.0 --- outline}

\author{Draft\\ Please Do Not Distribute}

%\author{Peter D. Karp\\
%Artificial Intelligence Center\\
%SRI International\\
%333 Ravenswood Ave.\\
%Menlo Park, CA  94025\\
%pkarp@ai.sri.com \\
%\  \\
%Thomas Gruber \\
%Knowledge Systems Laboratory \\
%Stanford University \\
%701 Welch Rd, Bldg C \\
%Palo Alto, CA  94304 \\
%gruber@hpp.stanford.edu
%}

\maketitle
\newpage

\tableofcontents
\newpage

\chapter*{Preface}

\chapter{Introduction}
(The author is TBD.)

Emphasize that syntax is prefix.  Arglist conventions are from Common
Lisp, but otherwise, spec is language independent.

Mention multiple back ends, multiple language bindings.

\section{The Need for GFP}

\section{The Proposed Solution}

\section{Design Objectives}

\chapter{Knowledge Model}
(To be written by RF except for the sections where other
authors are explicitly identified.)

Use FOL formalization wherever it makes sense.  use  tell/ask document
as a reference.

Include lots of simple concrete examples.  Especially to distinguish
between own/template slot/facet.  Look at Tutorial for some.

\section{Frames}

\section{Slots}

\section{Knowledge bases}

\section{Classes and Individuals}

\section{Inheritance}

\section{Defaults}

\section{Constraints}
(forward reference to the appendix being written by VKC)

\section{Facets}
(forward reference to the appendix being written by VKC)

\section{Behaviors}

\section{Standard Frame, Slot and Facet Names}

\section{Meta KB}
(To be written by JPR)

\section{Inference Model} 

\section{Behaviors of Representation Systems}

\subsection{Constraint Checking}
(Perhaps a forward reference to the appendix on constraint checking.)

\subsection{Facets}

\subsection{Defaults}

\subsection{Class Slot Types}

\subsection{Test Function}

\subsection{Collection Types}

\chapter{GFP Operations}

\section{Discussion on common arguments}
(To be put together by VKC.)

\section{Error Handling}
(To be put together by VKC.)

\subsection{Required vs Optional Errors}

\subsection{Condition Objects}

\subsection{Documented GFP Errors}
(Perhaps with a forward pointer to a chapter/appendix on 
a comprehensive list of errors.)

\section{Compliance Levels}
The taxonomy identifying the accessible frames for an FRS.  (Author
TBD.  I am not sure if this should go in the knowledge model.)

\section{Categories of GFP Operations}

\subsection{Operations on Frames}
(Informal discussion using the intermediate text from the current version of the spec)
(To be put together by VKC.)

\subsection{Operations on Classes}

\subsection{Operations on Instances}

\subsection{Operations on Facets}

\subsection{Operations on Slots}

\subsection{KB Operations}

\section{Enumerator Operations}
(To be written by AF.) 

\section{Format for Documentation of GFP operations}
(To be put together by VKC.)

\section{Alphabetical Listing of all GFP Operations}
(To be put together by JPR.)

\chapter{Function Specifiers}
(To be written by AF)

\chapter{Language Bindings}
(To be written by AF)

\appendix

\chapter{Facets, Slots}
(To be written by VKC)

\chapter{Implementations}
(Author TBD)

\bibliography{all}
\bibliographystyle{plain}

\printindex

\end{document}
